Fast Regression of the Tritium Breeding Ratio in Tokamak Fusion Reactors

### 2020-05-25 paper/ucl_tbr_paper.tex
add outline
do not use shortened email
add full introduction from the final report, ignore .out files
remove data exploration section
add full methodology section from the report
add bibliography from the report, ignore byproducts
smaller todos

\usepackage{iopams}
\usepackage{siunitx}
\usepackage[colorinlistoftodos]{todonotes} % TODO: remove me before submitting

\providecommand{\keywords}[1]{\textbf{\textit{Index terms---}} #1}

\begin{document}
\title[Fast Regression of the Tritium Breeding Ratio in Tokamaks]{Fast Regression of the
Tritium Breeding Ratio in Tokamak Fusion Reactors} % TODO: revise this

@@

% TODO: check if Graham can also have a shorter version of email
\eads{\mailto{graham.vangoffrier.19@ucl.ac.uk}, \mailto{petr.manek@ucl.ac.uk}}

@@

\todo{This is a comment that will appear in the margin}

>>>>

\usepackage{iopams}

\makeatletter
\@namedef{ver@amsmath.sty}{}
\makeatother

\usepackage{siunitx}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % TODO: remove me before submitting
\usepackage{isotope}
\usepackage{fixltx2e}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{url}

\providecommand{\keywords}[1]{\textbf{\textit{Index terms---}} #1}
\newcommand{\DDO}{D\textsubscript{2}O}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FRONT MATTER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[Fast Regression of the Tritium Breeding Ratio in Tokamaks]{Fast Regression of the
Tritium Breeding Ratio in Tokamak Fusion Reactors} % TODO: revise this

@@

\eads{\mailto{graham.vangoffrier.19@ucl.ac.uk}, \mailto{petr.manek.19@ucl.ac.uk}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MAIN MATTER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\label{sec:introduction}
\input{introduction}

\section{Methodology}
\label{sec:methodoglogy}
\input{methodology}

\section{Results}
\label{sec:results}
\input{results}

\section{Conclusion}
\label{sec:conclusion}
\input{conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BACK MATTER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Acknowledgements}
\label{sec:acknowledgements}
\input{acknowledgements}

\section{References}
\label{sec:references}
\bibliography{ucl_tbr_paper}
\bibliographystyle{iopart-num}
